Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2020-12-23 Latex/journal_v1/V2/pr.tex
journal change

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE in $v^{th}$ service experienced at slice $s$ on PRB $k$ which is obtained from
 $\rho_{u_i}^{k,s}$ is the SNR 
\begin{equation}\label{eq2}
\rho_{u_i}^{k,s} =  \sum_{r=1}^{R}\frac{|p_{r,u_i}^{k,s}{\bold{h}_{r,u_i}^{H \: k,s}} \bold{w}_{r,u_i}^{k,s} g_{u_i}^r|^2}{BN_0 + I_{r,u_i}^{k,s}},
\end{equation} 
where $p_{r,u_i}^{k,s}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE in $v^{th}$ service, served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u_i}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{r,u_i}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u_i}^{k,s} = {\bold{h}_{r,u_i}^{k,s}}({\bold{h}_{r,u_i}^{H \: k,s1}} {\bold{h}_{r,u_i}^{k,s}})^{-1}
\end{equation}
Moreover, $g_{u_i}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u_i}^{k,s1}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{r,u_i}^{k,s} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u_i}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u_i}^{k,s1} g_{u_i}^{r'}|^2}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{k,s}_{r,u_i}e^{k,s}_{r',u(v,l)}a_{u_i}a_{u(v,l)} b_{v, s} $
and $\gamma_{2} = e^{k,s}_{r,u_i}e^{k,n}_{r',u(y,l)}a_{u_i}a_{u(y,l)} b_{v, s} b_{y,n} $.
Where $a_{u_i} \in \{0,1\}$ is a binary variable to depict user admission.
$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
$e^{k,s}_{r,u_i}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.

>>>>

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{u(s,i)}^{k} =  \sum_{r=1}^{R}\frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u_i}^{k,s}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{r,u_i}^{k,s} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $v^{th}$ service that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u_i}^{k,s} = {\bold{h}_{r,u_i}^{k,s}}({\bold{h}_{r,u_i}^{H \: k,s1}} {\bold{h}_{r,u_i}^{k,s}})^{-1}
\end{equation}
Moreover, $g_{u_i}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE in $v_{1}^{th}$ service or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u_i}^{k,s1}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{r,u_i}^{k,s} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{v}} \gamma_{1}  p_{u_i}^{k,s}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u_i}^{k,s1} g_{u_i}^{r'}|^2}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u(y,l)}^{k,n}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u_i}^{H \: k,s}} \bold{w}_{r',u(y,l)}^{k,n} g_{u(y,l)}^{r'}|^2}_{\text{(inter-service interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{k,s}_{r,u_i}e^{k,s}_{r',u(v,l)}a_{u_i}a_{u(v,l)} b_{v, s} $
and $\gamma_{2} = e^{k,s}_{r,u_i}e^{k,n}_{r',u(y,l)}a_{u_i}a_{u(y,l)} b_{v, s} b_{y,n} $.
Where $a_{u_i} \in \{0,1\}$ is a binary variable to depict user admission.
$b_{v, s}$ is a binary variable that illustrates whether slice $s$ is allocated to service $v$ or not. 
$e^{k,s}_{r,u_i}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in service $v$, assigned to $r^{th}$ o-RU using slice $s$ or not.
